|

### 2020-03-04 analysis/paper/manuscript.Rmd
Add new section to the discussion on 'bespoke to general tools'

Quantitative stock assessment plays a central role in modern fisheries management [@hilborn1992]. Over time, and as new methods are developed, there is an increasing amount of data available to inform stock assessments. These data might be richer information on stock structure using an increasing array of markers and biomarkers, and/or the continued lengthening of population status and catch time series. Concurrently, analytical methods are now able to integrate many data sources into one stock assessment model [@maunder2013]. While these advances have surely improved the advice provided at stock assessments, it has become more difficult to communicate the basis of this advice in a meaningful way. Visualisation play a critical role in communicating this information to stakeholders [@levontin2017], however, traditional formats (e.g. slides) are often insufficient to convey the richness of information available and the static and sequential nature of these formats can stifle meaningful discussions. A solution to this problem is the effective use of interactive visualization tools [@keena2016]. These are common tools we use every day on a range of web sites, but their use is no longer restricted to web site developers as these tools are being integrated into software commonly used by the research community [@perkel2018]. As a result, an increasing number of scientists across a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [e.g. @jones2016; @yeatman2018; @letcher2018].

@@

# Generic vs. bespoke

The tools highlighted here were custom built to solve data visualization challenges that are common to many fisheries management organizations.

@@

All code used to generate this paper, Supplement 1 ("Getting Started" dashboard) and Supplement 2 ("NCAM explorer" dashboard) are available at https://github.com/PaulRegular/interactive-stock-assessment.

>>>>

Quantitative stock assessment plays a central role in modern fisheries management [@hilborn1992]. Over time, and as new methods are developed, there is an increasing amount of data available to inform stock assessments. These data might be richer information on stock structure using an increasing array of markers and biomarkers, and/or the continued lengthening of population status and catch time series. Concurrently, analytical methods are now able to integrate many data sources into one stock assessment model [@maunder2013]. While these advances have surely improved the advice provided at stock assessments, it has become more difficult to communicate the basis of this advice in a meaningful way. Visualizations play a critical role in communicating this information to stakeholders [@levontin2017], however, traditional formats (e.g. slides) are often insufficient to convey the richness of information available and the static and sequential nature of these formats can stifle meaningful discussions. A solution to this problem is the effective use of interactive visualization tools [@keena2016]. These are common tools we use every day on a range of web sites, but their use is no longer restricted to web site developers as these tools are being integrated into software commonly used by the research community [@perkel2018]. As a result, an increasing number of scientists across a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [e.g. @jones2016; @yeatman2018; @letcher2018].

@@

# From bespoke to general tools

The interactive tools highlighted here were custom built to solve data visualization challenges that are common to many fisheries management organizations. Consequently, there exists the possibility of generalizing these tools to simplify their application to other regions. Region specific data management and modelling approaches, however, will surely complicate matters as tools built for one region may be difficult to apply in another region. Even within our own region, different approaches and needs meant that the code behind NCAM explorer (Supplement 2) required modifications to be applied to another model being developed. Nevertheless, considerable chunks of code could be recycled and, in the process, new features were added to allow the visualization of multiple model configurations within the one dashboard. This effort was one step forward in improving the generality of the tool and another step, which is actively being worked on by a colleague in IFREMER, is to modify the tool to visualize output from SAM, a state-space stock assessment model widely used to assess ICES stocks [@nielsen2014]. Though more time is required to make the dashboard code more general as the developer must ensure the code is robust to a wider range of scenarios, substantial value could be added by making it more widely applicable. Likewise, the concept behind RStrap Explorer and the tagging tool could be applied to other regions and the most efficient approach may be to build upon existing general frameworks [e.g. StoX software; @johnsen2019]. These are, of course, early days in the development and application of interactive tools to stock assessment. Because the tools we highlight are themselves general, flexible and accessible, we suspect that bespoke applications will continue to be developed in parallel with more general stock assessment dashboards. Regardless of the approach, it is important that the path taken is transparent and reproducible.

@@

All code used to generate this paper, Supplement 1 (getting started dashboard) and Supplement 2 (NCAM explorer) are available at https://github.com/PaulRegular/interactive-stock-assessment.
